Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-09 WSSSPE3/report/wg_appendix_publishing_SW.tex
minor changes/comments in publishing sections moved some credit text to be a general intro to the section
Fix typos

A tentative first cut at the list containing executable papers identified the following:
\begin{itemize}
\item ACM Transactions on Mathematical Software (TOMS): provides the extra step
 of having reviewers validate the code which was submitted with the publication.
\item The Mathematica Journal: publishes Mathematica notebooks (with equations,
figures, etc.) directly.
\item O'Reily Media: announced that it plans to make IPython Notebooks a first-class
 authoring environment for their publishing program alongside their existing mechanisms.
\item Nature: offering a list of notebooks published alongside more traditional articles,
 and is looking at ways to make these documents more official. There are, in fact, a
 number of journals that offer ``electronic supplements'' to the more traditionally published
 static articles.
\item IPython: maintained list of ``reproducible academic publications''~\cite{ipython-pubs}.
\item KBase: narratives build on IPython\slash Jupyter notebooks to build publications that are
  reproducible, and can be commented or annotated.
\end{itemize}

@@

Create the first version of the web page to be displayed on the Software Sustainability
Institute's website.

>>>>

A tentative first cut at the list containing executable papers identified the following:
\begin{itemize}
\item ACM Transactions on Mathematical Software (TOMS): provides the extra step
 of having reviewers validate the code which was submitted with the publication.
\item The Mathematica Journal: publishes Mathematica notebooks (with equations,
figures, etc.) directly.
\item O'Reilly Media: announced that it plans to make IPython Notebooks a first-class
 authoring environment for their publishing program alongside their existing mechanisms.
\item Nature: offering a list of notebooks published alongside more traditional articles,
 and is looking at ways to make these documents more official. There are, in fact, a
 number of journals that offer ``electronic supplements'' to the more traditionally published
 static articles.
\item IPython: maintained list of ``reproducible academic publications''~\cite{ipython-pubs}.
\item KBase: narratives build on IPython\slash Jupyter notebooks to build publications that are
  reproducible, and can be commented or annotated.
\end{itemize}

@@

Create the first version of the web page to be displayed on the Software Sustainability
Institute's website: \url{http://www.software.ac.uk}. \katznote{when?}
